Classless Java

### 2016-03-24 OOPSLA16/sections/CaseStudy.tex
table small fix

\vspace{0.5em}
\begin{tabular}{llll}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
old (\texttt{eval})         & 626  & new (\texttt{eval})         & 560  \\ 
\rowcolor[HTML]{C0C0C0}
old (\texttt{eval} + \texttt{print}) & 661  & new (\texttt{eval} + \texttt{print}) & 677  \\ \hline
\end{tabular}

>>>>

\vspace{0.5em}
{\small
\begin{tabular}{llll}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
original (\texttt{eval})         & 626  & original (\texttt{eval}+\texttt{print}) & 661  \\ 
\rowcolor[HTML]{C0C0C0}
refactored (\texttt{eval})         & 560  & refactored (\texttt{eval}+\texttt{print}) & 677  \\ \hline
\end{tabular}
}
